Generalised gravitational burst generation with Generative Adversarial Networks

### 2020-09-03 Paper_draft/main.tex
Finished my comments

@@

@@

\begin{itemize}
\item Begin by outlining the type of results you will be presenting
\item A subsection on the general quality of generated waveforms - we may need
to have overlaps between generated wavefoms and training data (maybe)
\item A subsection on the descriminator - maybe a confusion matrix?
\item a subsection on the latent space varaition within each class - fixed
class, sliding in latent space.
\item A subsection on the class space variation - fixed latent space and
sliding in the class space.
\item A final subsection on the general waveform model based on random latent
and class space locations.
\item Make no conclusions.
\end{itemize}
\end{comment}

Given a 100 dimensional vector drawn from a normal distribution and a class label, the GAN is able to generate burst-like waveforms  generalised from the training set. We set out by describing the quality of generated waveforms and how they compare to the training set. We then explore the structure of the latent and class spaces by interpolating between points in these spaces. We test  two methods of sampling from the class space that can be used to generate a new breed of signal by merging two or more families together.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/generations/sg.png}
    \includegraphics[width=\textwidth]{figures/generations/rd.png}
    \includegraphics[width=\textwidth]{figures/generations/wnb.png}
    \includegraphics[width=\textwidth]{figures/generations/blip.png}
    \includegraphics[width=\textwidth]{figures/generations/bbh.png}
    \caption{Examples of \ac{GW} burst signals generated by a conditional generative adversarial network. By row: Sine-Gaussian, Ringdown,
White-noise burst, Gaussian pulse, Binary black hole merger.}
\label{fig:gen_signals} \end{figure}

\subsection{Signal generation}
The generator network is a function G : $\mathbf{z},\mathbf{c} $ $\in$ $\mathbb{R}^{100}$ $\to$ $\mathbb{R}^{1024\times2}$, where $\mathbf{z},\mathbf{c}$ are the latent vector and class vector. Given a latent vector randomly sampled from a normal distribution with zero mean and unit variance, a class label which is represented by a 5 dimensional one-hot encoded vector for each class, the results from the generator can be seen in \cref{fig:gen_signals}. Each plot shows the output of the generator after given randomised $\mathbf{z}$ and one of the five class vectors $\mathbf{c}$.
 %Depending on the orientation of the detector with respect to a hypothetical signal in the sky, the waveforms may appear inverted, shifted in time and their strain attenuated.

\subsection{Interpolation}
Machine learning algorithms are often described as universal function approximators. In the generators case it maps samples drawn from a 100 dimensional Gaussian space to its representation of the training set. As with any function, there should be a one to one mapping from the domain and co-domain to allow for smooth transitions across the latent space. One advantage of using GANs as a waveform generator is that once it is trained, it can perform rapid generations faster than computationally
expensive algorithms \michael{e.g.?}. For complicated data sets, the network architecture must be diverse and dense enough to capture distinct variations from the training set. Most GANs perform well on relatively low resolution image generations, however, higher resolutions demand larger networks and long training times. GANs attempting to replicate complicated structures and do not have the necessary architecture either struggle to produce results at all or fall into the common failure mode know as mode collapse; where the generator produces a small variety of samples or simply memorises the training set. To test this, we perform linear interpolations in the latent and class space.

In this section we explore the latent space formed by the generator by interpolation. We take two random points in the latent space and linearly interpolate between them. These new latent space vectors can now be fed into the generator to make predictions on while keeping the class vectors constant. The full effect shown in \cref{fig:z_interp}. We can see that each plot shows plausible waveforms suggesting that the generator has constructed a smooth space unlike the discrete training case. Additionally as each class is given the same latent points to interpolate over, we can see that the waveforms cluster together with respect to their parameters. Visually, the sine-gaussian and ring-down waveforms share similar frequencies and the other signals show similar decays and starting epochs. The only exception is BBH waveforms, which is expected as they were trained with more variety of parameters and consistently have their peaks in the last quarter of the time series.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/generations/z_interp_sg.png}
    \includegraphics[width=\textwidth]{figures/generations/z_interp_rd.png}
    \includegraphics[width=\textwidth]{figures/generations/z_interp_wnb.png}
    \includegraphics[width=\textwidth]{figures/generations/z_interp_blip.png}
    \includegraphics[width=\textwidth]{figures/generations/z_interp_bbh.png}
    \caption{Latent space linear interpolation, class space is constant.}
    \label{fig:z_interp}
\end{figure}

\subsubsection{Class space interpolation}
In order to explore the class space we keep the latent vector constant and interpolate through the 5 classes. We construct a path between the 5 waveforms and show that the space is populated enough to allow for transitions between classes. Sine-Gaussian to ringdown performs well in interpolation with each signal being a plausible burst GW. It is obvious that the GAN has clustered these two groups during training as they share many characteristics. The other signals have sharper transitions but still retain plausible looking waveforms.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/generations/interp_blip-sg.png}
    \includegraphics[width=\textwidth]{figures/generations/interp_wnb-rd.png}
    \includegraphics[width=\textwidth]{figures/generations/interp_sg-bbh.png}
    \caption{Class space linear interpolation, class space is held constant. Top row: gaussian blip to sine-gaussian, middle row: white noise burst to ringdown, bottom row: sine-gaussian to BBH.}
    \label{fig:c_interp}
\end{figure}

\subsection{Using a GAN to generate unmodelled waveforms}
So far the analysis has focused on interpolating between two classes of signals with the aim to use the interpolated signals as unmodelled waveforms, instead, we may consider random mixtures of classes. We defined the classes in one-hot encoding framework, that is, each class resides at the corner points of a 5 dimensional cube. In order to generate an even mixture of classes we sample points uniformly in this space. \jordan{this would be the box}. Alternativly we can sampe points from the plane that intersects the four corners, which for a 5-dimensional case is, sample from a 4-simplex. Thks can nbee seen in \ref{fig:unmodelled_samples}. \jordan{why? this enforces the vector points to sum to one. Why is that good? Well it keeps the points lying on the simplex.}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/generations/simplex_sample1.png}
    \includegraphics[width=\textwidth]{figures/generations/simplex_sample2.png}
    \includegraphics[width=\textwidth]{figures/generations/simplex_sample3.png}

    \includegraphics[width=\textwidth]{figures/generations/uniform_sample3.png}
    \includegraphics[width=\textwidth]{figures/generations/uniform_sample2.png}
    \includegraphics[width=\textwidth]{figures/generations/uniform_sample1.png}
    \caption{GAN generations where the class vectors are sampled from the 4-D plane and sampled uniformly in the class space.}
    \label{fig:unmodelled_samples}
\end{figure}

\begin{comment}
We can now think of ways to properly sample from the space between these points in a uniform way. Uniformity enforces the condition that we have a variety of waveforms. Thge easiest being to uniformly sample points in this space and use them as the class vectors for the generator. Another way would be to keep the magnitude of the class vector as 1. For a 5-dimensional space we would sample from the 4-dimensional plane that intersects the corner points. 
\end{comment}

\michael{We don't show any results with two detectors yet we use two detectors for the CNN, we might want to think when/where it's best to show some generations with both detectors. Maybe when we show a signal with noise since it's all part of the post-processing?}

\subsection{CNN analysis}
In this section of the analysis we will forensically compare generations from the GAN to help determine the success and failures of the model. We investigate a simple case of using a CNN to detect whether a signal is contained in noise or if the data is noise only. The signals we train the CNN on are generated from the GAN with their latent input randomised from a 100-dimensional Gaussian distribution and are categorised by their method of defining their class vector: 
\begin{itemize}
	\item Conditional – Definite categorical generations from the GAN. These signals are the closest to the training set.
	\item Uniform – Generated using a uniform distribution U[0,1] as the input class vector.
	\item Simplex – Generated using a Dirichlet distribution that samples from the 4-simplex as the input class vector. 
\end{itemize}
The CNN is trained to distinguish between two classes: signals in additive Gaussian noise and Gaussian noise, where “signals” are taken from either the Conditional, Uniform or Simplex cases. This means in total there are three CNNs to train and all CNNs share the same architectural structure. All of the training data used is “whitened” by a power spectral density (PSD) at Advanced LIGO design sensitivity, such that, there is equal power at each frequency and is correctly normalised. This procedure is applied to signals whose signal-to-noise ratios (SNRs) are defined prior to be in the range uniformly [1-16]. For each run the training data consists of 200,000 signals which contain one half noise only and one half signal contained in noise. Of that 80\% is used for training and 20\% used for validation. A different testing set is also used in analysis that is 200,000 in size.

*table of parameters used for CNN*

In Fig. \ref{fig:roc_curves} we compare the CNN results between the three datasets, we train three CNNs on the Conditional, simplex and uniform data sets and use these models to make predictions on the other unseen datasets. We make a comparison by fixing the fraction of samples incorrectly identified as signals (false alarm rate) and plotting this versus the optimal SNR of the signals.

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{figures/conditional_trained.png}
    \includegraphics[width=0.8\textwidth]{figures/simplex_trained.png}
    \includegraphics[width=0.8\textwidth]{figures/uniform_trained.png}

    \caption{Efficiency curves comparing the performance of CNNs trained on conditional generations (top), simplex generations (middle), uniform generations (bottom) for a fixed false alarm rate of $10^{-3}$.}
    \label{fig:roc_curves}
\end{figure}

These results show for a CNN trained on conditional signals, the uniform data set is distinguishable from the conditional and simplex dataset. The CNN is robust enough to capture the differences between the datasets and shows that the GAN can generate a variety of unmodelled waveforms that can be used in future testing.

\begin{comment}
{\subsection{Vector Arithmetic}
In DCGANs the authors demonstrated unsupervised vector arithmetic with celebrity face generation. They kept points in the latent space and performed simple vector arithmetic to generate new images. This allows for intuitive and targeted generation of images. However, the authors realised that single images vectors were unstable and there was a need to average three vectors before any arithmetic. DCGANs is unconditional, therefore, the vectors used were chosen empirically, generating many faces and choosing the attributes for study. Here, we show that this GAN only needs a single vector representation and due to conditioning we can have more control over which vectors to use in the arithmetic. In \cref{fig:arithmetic} we generate a whitenoise burst and a BBH insprial using their respective class labels and use a randomised latent point and response. Keeping the latent point and response, we average the two class vectors and use this as input to the generator. \Cref{fig:arithmetic} (c) shows the generation based on the combined class vectors which visually looks similar to a supernova waveform. Supernova waveform generations require expensive numerical relativity simulations and various assumptions about the collapse of its parent star. Here, we are able to produce similar waves at a fraction of the expense and we are able to further modify the resultant by using different latent space samples. \jordan{this is the adding noise thing but i need to work out the correct way to do it with the directional vector}. 
\end{comment}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In this work we present the potential of Generative Adversarial Networks for burst ac{GW} analysis. We have shown that GANs have the ability to generate 5 class varieties of modelled burst \ac{GW} signals that can be generated at whim. The latent and class spaces were explored through interpolation and suggest that the space provides smooth translations between classes and overall waveform shape. We then showed targeted waveform generation by mixing classes to produce new unmodlled waveform varieties that can be used to test current burst search pipelines. \jordan{couple of sentences about classifier}.

In order to extend this work to a viable burst wave generator and classifier a few points require further research. In principle it is trivial to add another detector inside the response layer \jordan{response is the wrong thing to say since the time delay isnt really a response, extrinsic layer? just non trainable layer? The box?}, however, as this now 3 dimensional signal is feed to the discriminator this will no doubt require further tweaking of the network. We can add more burst-like wave forms in the training set, like detector glitches which would similarly require further network design. The work presented here is noise free. To havea complete generation and detection package we would like to train the network on signals hidden in additive Gaussian noise and test the ability of the auxiliary classifier.

The approach shown in this work shows promise in generating unmodelled burst waveforms from exotic sources. Having the ability to quickly generate new waveforms is essential to test current detection schemes and their susceptibilty to unmodelled sources. We belive that GANs have the ability to generate high fidelity waveforms at a fraction of the computational expense and do not rely on large prior parameter space. Having banks of these waveforms at hand can aid in our understand of the physics processes behind these non-standard ac{GW} emitters.

>>>>

~\chris{there needs to be some more discusiion of what the latent space
and $z$ variables represent in the GAN in general. It maps the intrinsic
variation of the training space onto the Gaussian latent space distribution.}

@@

~\chris{After describing the latent space meaning in the GAN section you need
to bring that together with a discussion of the entirely seperate class space
and how it is defined with reference to the on-hot encoded corners of a 5-D
vector space. Here is where you can inroduce the concept of the space and
mention the issue of probing the regions between the corners}

@@

\begin{comment}
\begin{itemize}
\item Begin by outlining the type of results you will be presenting
\item A subsection on the general quality of generated waveforms - we may need
to have overlaps between generated wavefoms and training data (maybe)
\item A subsection on the descriminator - maybe a confusion matrix?
\item a subsection on the latent space varaition within each class - fixed
class, sliding in latent space.
\item A subsection on the class space variation - fixed latent space and
sliding in the class space.
\item A final subsection on the general waveform model based on random latent
and class space locations.
\item Make no conclusions.
\end{itemize}
\end{comment}

% describe the main idea
%
Given a 100-dimensional vector drawn from a normal distribution and a class
label, the GAN is able to generate burst-like waveforms generalised from the
training set~\chris{please state this in terms of the latent space and class
space}. We set out by describing the quality of generated waveforms and
how they compare to the training set. We then explore the structure of the
latent and class spaces by interpolating between points in these spaces. We
test two methods of sampling from the class space that can be used to generate
a new breed of signal composed of weighted elements of each training class.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/generations/sg.png}
    \includegraphics[width=\textwidth]{figures/generations/rd.png}
    \includegraphics[width=\textwidth]{figures/generations/wnb.png}
    \includegraphics[width=\textwidth]{figures/generations/blip.png}
    \includegraphics[width=\textwidth]{figures/generations/bbh.png}
    \caption{Examples of \ac{GW} burst signals generated by a conditional generative adversarial network. By row: Sine-Gaussian, Ringdown,
White-noise burst, Gaussian pulse, Binary black hole merger.~\chris{please add
lots more description to the caption regarding wjhat you are plotting. Mention
that these are generated waveforms plotted as a function of time, latent space
values are randomised for each panel (or are they the same for each column?)
classes on each row. Also mention the zoom in on the time axis. Also fix the
time axis limits so they are consistent across all waveforms.}}
\label{fig:gen_signals} 
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Known class signal generation}

The generator network is a function $G$ : $\mathbf{z},\mathbf{c} $ $\in$
$\mathbb{R}^{100}$ $\to$ $\mathbb{R}^{1024\times2}$,~\chris{why is this
outputting to 2 timeseries? Is this out of date?} where $\mathbf{z},\mathbf{c}$
are the latent vector and class vector~\chris{these have already been defined
}. Given a latent vector randomly sampled from a normal distribution with zero
mean and unit variance, a class label which is represented by a 5 dimensional
one-hot encoded vector for each class~\chris{give an example e.g.
$c=[0,1,0,0,0]$ represents the ring-down signal class}, the results from the
generator can be seen in \cref{fig:gen_signals}~\chris{please indicate that
this is all done after training has completed}. Each plot shows the output of
the generator for random input latent space vectors $\mathbf{z}$ and each row
corresponds to one of the five class vectors $\mathbf{c}$.~\chris{yes? What
about the plot? Anything positive to say about what you're showing? Please
comment on the quality of the generated waveforms and the good varaition within
each class representative of the variation in the training data. The point is
to show the general variation and quality.}

\chris{You also need to make it clear somewhere (maybe here) that you are
generting single polarisation waveforms with normalised amplitude fixed to
unity.}

\chris{Also, how is the reader going to judge that your waveforms are good if
we don't show any examples of the training data. I recommend a single plot
showing 5 waveforms (5 panels horizontally) for reference.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Interpolation within the latent space}

% expain what we are planning to show here
%
\ac{ML} algorithms are often described as universal function approximators. In
the case of the generator it maps samples drawn from a 100 dimensional Gaussian
distribution in the latent space to its representation of the training set. As
with any function, there should be a one to one mapping from the domain and
co-domain to allow for smooth transitions across the latent space. One
advantage of using \acp{GAN} as a waveform generator is that once it is
trained, it can perform rapid generations faster than computationally expensive
algorithms \michael{e.g.?}~\chris{you can maybe reference Seb Kahn and Green
here soon. It will be on the arXiv next week I think - they did fast CBC
waveform generation.  Also Walter Del Pozzo has a paper xoming out soon on
this. Neither use GANs though, just ML}. For complicated data sets, the network
architecture must be diverse and dense enough to capture distinct variations
from the training set.  Most GANs perform well on relatively low resolution
image generations, however, higher resolutions demand larger networks and long
training times. GANs attempting to replicate complicated structures and do not
have the necessary architecture either struggle to produce results at all or
fall into the common failure mode know as mode collapse; where the generator
produces a small variety of samples or simply memorises the training set. To
test this, we perform linear interpolations in the latent and class
space.~\chris{lots of technical talk before actually saying what you are trying
to do. Reverse this. Also try to provide references for the technical talk}

\chris{this paragraph should come before the other one since it explains what
you are doing before going into technical stuff} In this section we explore the
latent space formed by the generator by interpolation. We take two random
points in the latent space and linearly interpolate between them~\chris{OK, but
how do you select the latent points? Are they the same pair of points for each
class?}. These new latent space vectors can now be fed into the generator to
make predictions on~\chris{"to make predictions on" - what does that mean?}
while keeping the class vectors constant at each of the 5 \chris{fiducial?}
training classes. The full effect shown in~\cref{fig:z_interp}~\chris{not a
sentence}. We can see that each plot shows plausible waveforms suggesting that
the generator has constructed a smooth space unlike the discrete training
case~\chris{don't confuse the issue by saying that the class space is discrtee
when later we want to show the opposite}. Additionally as each class is given
the same latent points to interpolate over, we can see that the waveforms
cluster together with respect to their parameters. Visually, the sine-gaussian
and ring-down waveforms share similar frequencies and the other signals show
similar decays and starting epochs for a common latent space input. The only
exception is for the \ac{BBH} waveforms. This can be explained by the fact that
they were trained with more variety of parameters~\chris{what is more variety
of parameters? Does it really mean anything?} and consistently have their peak
amplitudes in the last quarter of the time series~\chris{do they? In the plot
the peak amplitude locations seem to range from 0.6 back to 0.5 but that's not
too different to the ring-downs, the white noise or the pulse. The
sine-Gaussian is the one that stands out as different. Can you please verify
the correctness of the plot you are referring to.}.

\chris{I think that it might be sensible to hand-pick the latent space
locations as the origin and the point $[1,1,\ldots,1]/2$. When you do random
locations we don't know what we should expect to get.}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/generations/z_interp_sg.png}
    \includegraphics[width=\textwidth]{figures/generations/z_interp_rd.png}
    \includegraphics[width=\textwidth]{figures/generations/z_interp_wnb.png}
    \includegraphics[width=\textwidth]{figures/generations/z_interp_blip.png}
    \includegraphics[width=\textwidth]{figures/generations/z_interp_bbh.png}
    \caption{Latent space linear interpolation, class space is
constant.~\chris{lots more discription needed. what is being plotted against
what? What is being held fixed, what is being varied.}}
    \label{fig:z_interp}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Interpolation between pairs of classes}

In order to explore the class space we keep the latent vector constant and
interpolate through the 5 classes. We construct a path between the 5 waveforms
and show that the space is populated enough to allow for transitions between
classes. Sine-Gaussian to ringdown performs well in interpolation with each
signal being a plausible burst GW. It is obvious that the GAN has clustered
these two groups during training as they share many characteristics. The other
signals have sharper transitions but still retain plausible looking waveforms.

~\chris{this is one of  the most important sections of the paper and there
is barely 1 paragrpah about it. Please beter explain what you are doing in
general when you fix the latent space location and explore the class space. The
concept of having arbitrary points in the 5-D class space should have been made
clear earlier on in the CGAN section (or elsewhere). There also isn't currently a
reference to the corresponding figure.}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/generations/interp_blip-sg.png}
    \includegraphics[width=\textwidth]{figures/generations/interp_wnb-rd.png}
    \includegraphics[width=\textwidth]{figures/generations/interp_sg-bbh.png}
    \caption{Class space linear interpolation, class space is held
constant~\chris{no it isn't}.
Top row: gaussian blip to sine-Gaussian, middle row: white noise burst to
ringdown, bottom row: sine-Gaussian to BBH.~\chris{Again, more description,
start from the basics, what is plotted against what. Is the latent space fixed
the same for each row? Add the class space vectors on each panel. We have 5
classes and so there are 10 possible pairs but you can't fit 10 rows here so
why do 3? Why not 5 or 6? }}
    \label{fig:c_interp}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{General interpolsation within the class space}

So far the analysis has focused~\chris{not really focussed, you only dedicated
1 paragraph to it in the previous subsection} on interpolating between two
classes of signals with the aim to use the interpolated signals as unmodelled
waveforms, instead, we may consider random mixtures of classes~\chris{don't
sell this according to our thought processes as we did the research, sell it as
"we just explained the pair interpolation since it's a stepping stone to the
general interpolation"}. We defined the classes in one-hot encoding framework,
that is, each class resides at the corner points of a 5 dimensional
cube~\chris{this should have already been stated n earlier sections}. In order
to generate an even mixture~\chris{by definition, it won't be an even mixture
if points are randomly sampled} of classes we sample points uniformly in this
space. \jordan{this would be the box}. Alternativly we can sampe points from
the plane that intersects the four corners, which for a 5-dimensional case is,
sample from a 4-simplex.~\chris{please dedicate an entire paragraph to the
simplex and box explanation. You may even need an equation or 2.} This can be
seen in~\ref{fig:unmodelled_samples}. \jordan{why? this enforces the vector
points to sum to one. Why is that good? Well it keeps the points lying on the
simplex.}~\chris{indeed. The reasons were originally that the plane is the
simplest structure (a hyper-surface or manifold if you;re being fancy) in the
class space that intersects all classes and has a symmetry such that no class
is favoured over any other - however that property is largely due to the
locations within the one-hot encoding space. Sampling from the simplex can be
seen as sampling from between the classes - truly interpolating within the
space. Alternatively, the cube is not the simplest space since it contains
points up to a distance of unity from the closst class e.g. [0,0,0,0,0] is a
distance of 1 away from all classes (as is [1,1,1,1,1]). This space contains
the simplex as a subspace but also allows for some level of extrapolation.
Hence we would expect the unexpected in the cube and hope for less surprises
with the simplex. THere is also the possibility of exploring outside the cube.
}

~\chris{Also, discuss the corresponding figure! There has to be comment on the
features of simplex vs box generations as well as general comments about how
the GAN likes to mix signals up. Pick on specific examples and comment on
interesting or annoying features.}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/generations/simplex_sample1.png}
    \includegraphics[width=\textwidth]{figures/generations/simplex_sample2.png}
    \includegraphics[width=\textwidth]{figures/generations/simplex_sample3.png}
    \includegraphics[width=\textwidth]{figures/generations/uniform_sample3.png}
    \includegraphics[width=\textwidth]{figures/generations/uniform_sample2.png}
    \includegraphics[width=\textwidth]{figures/generations/uniform_sample1.png}
    \caption{GAN generations where the class vectors are sampled from the 4-D
plane and sampled uniformly in the class space.~\chris{As always, far more
description needed. What are you plotting against what? Do you fix or randomise
the latent space locations? You absolutely need to specify which are simplex
and which are box.}}
    \label{fig:unmodelled_samples}
\end{figure}

~\chris{I have an idea for the plots. Could we have a colour coding system
where each class gets a colour and then when you mix them you plot it with the
mixed colours - you average the RGB values. Maybe everything would look brown?
Worth a try?}

% remove these comments
%
\begin{comment}
We can now think of ways to properly sample from the space between these points
in a uniform way. Uniformity enforces the condition that we have a variety of
waveforms. Thge easiest being to uniformly sample points in this space and use
them as the class vectors for the generator. Another way would be to keep the
magnitude of the class vector as 1. For a 5-dimensional space we would sample
from the 4-dimensional plane that intersects the corner points.  \end{comment}

\michael{We don't show any results with two detectors yet we use two detectors
for the CNN, we might want to think when/where it's best to show some
generations with both detectors. Maybe when we show a signal with noise since
it's all part of the post-processing?}~\chris{I agree, see my comment in the
CNN section next.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Searching for generalised burst - a CNN analysis}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In this section of the analysis we will forensically~\chris{no we won't}
compare different waveform generations from the \ac{CGAN} to help determine the
success and failures of the model~\chris{what does this mean? What model?}. We
investigate a simple case using a \ac{CNN} to detect whether a signal is
contained in noise or if the data contains noise only. The signals we use to
train the \ac{CNN} are generated from the \ac{GAN} with their latent input
randomised from a 100-dimensional Gaussian distribution~\chris{yes, but this
should be obvious since we never deviate from the 100-D latent vector approach}
and are categorised by the method used to sample from the class space. These
methods are divided into the following:

\begin{itemize}
%
\item {\bf Conditional}: Definite categorical generations~\chris{yes, but what
does that mean. You've never mentioned that phrase before} from the \ac{GAN}.
These signals are the closest to the training set.
%
\item {\bf Uniform}: Generated using a uniform distribution U[0,1] as the input
class vector~\chris{yes, but you need to specify the 5-D nature of the space}.
%
\item {\bf Simplex}: Generated using a Dirichlet distribution that samples from the
4-simplex as the input class vector and includes within it the conditional
locations.~\chris{all fine as long as you have defined the 4-simplex earlier
on.} 
%
\end{itemize}

\chris{please add an example plot showing the normalised and whitened input of
an SNR=8 signal, one panel for each detector, with noisy signal and noise-free
signal plotted on top. Then remember to reference it in the text.}

The CNN~\chris{whoah, hold on. What CNN? You said you were going to use one but
can we get a few more details first. what's the input, what's the output,
what's the loss function, then point us to a table of params in the appendix.}
is trained to distinguish between two classes: signals in additive Gaussian
noise and Gaussian noise, where “signals” are taken from either the
Conditional, Uniform or Simplex cases~\chris{the signals+noise and noise
statement is repetetive of the previous paragraph.}. This means in total there
are three \acp{CNN} to train and all \acp{CNN} share the same architectural
structure. All of the training data used is whitened using the Advanced LIGO
design sensitivity \ac{PSD}, such that there is equal noise power at each
frequency and the data is correctly normalised~\chris{but what is correctly
normalised. Remember trhat we have to be reproducible so you have to make sure
that someone reading this can repeat your experiment.}. This procedure is
applied to signals whose \acp{SNR} are sampled uniformly in the range $[1-16]$.
For each run~\chris{what is a run} the training data consists of $2\times 10^5$
signals which contain one half noise only and one half signal contained in
noise. Of that, 80\% is used for training and 20\% used for validation. A
different testing set is also used in the analysis that is $2\times 10^5$ in
size.~\chris{This final sentence is worded strangely but also why do we have
such a large testing set? I can only imagine that we did this so that we could
go to small $\sim 10^{-5}$ false alarm rates. Is that right?}

\chris{there is no mention of the "old" box, the one that randomised the sky
location, time shifted the signals and applied the antenna patterns. Also no
mention of multi-detector data and no mention of use of channels. Please add
all of this. }

*table of parameters used for CNN*~\chris{put this in the appendix with the
GAN table}

In~\cref{fig:roc_curves} we compare the \ac{CNN} results between the three
datasets, we train three \acp{CNN} on the Conditional, simplex and uniform data sets
and use these models to make predictions on the other unseen datasets. We make
a comparison by fixing the fraction of samples incorrectly identified as
signals (false alarm rate) and plotting this versus the optimal SNR of the
signals.~\chris{this last sentence isn't quite right}

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{figures/conditional_trained.png}
    \includegraphics[width=0.8\textwidth]{figures/simplex_trained.png}
    \includegraphics[width=0.8\textwidth]{figures/uniform_trained.png}
    \caption{Efficiency curves comparing the performance of \acp{CNN} trained on
conditional generations (top), simplex generations (middle), uniform
generations (bottom) for a fixed false alarm rate of $10^{-3}$.~\chris{more
description. What is plotted against what? The fonts are different to the other
plots. The y-axis is not a rate but a prbability (a FAP unfortunately)}}
\label{fig:roc_curves} 
\end{figure}

These results show for a \ac{CNN} trained on conditional signals, the uniform data
set is distinguishable from the conditional and simplex dataset. The \ac{CNN} is
robust enough to capture the differences between the datasets and shows that
the GAN can generate a variety of unmodelled waveforms that can be used in
future testing.

~\chris{please write more about the results of the CNN}

% remove this comment if not being used
\begin{comment}
{\subsection{Vector Arithmetic}
In DCGANs the authors demonstrated unsupervised vector arithmetic with celebrity face generation. They kept points in the latent space and performed simple vector arithmetic to generate new images. This allows for intuitive and targeted generation of images. However, the authors realised that single images vectors were unstable and there was a need to average three vectors before any arithmetic. DCGANs is unconditional, therefore, the vectors used were chosen empirically, generating many faces and choosing the attributes for study. Here, we show that this GAN only needs a single vector representation and due to conditioning we can have more control over which vectors to use in the arithmetic. In \cref{fig:arithmetic} we generate a whitenoise burst and a BBH insprial using their respective class labels and use a randomised latent point and response. Keeping the latent point and response, we average the two class vectors and use this as input to the generator. \Cref{fig:arithmetic} (c) shows the generation based on the combined class vectors which visually looks similar to a supernova waveform. Supernova waveform generations require expensive numerical relativity simulations and various assumptions about the collapse of its parent star. Here, we are able to produce similar waves at a fraction of the expense and we are able to further modify the resultant by using different latent space samples. \jordan{this is the adding noise thing but i need to work out the correct way to do it with the directional vector}. 
\end{comment}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% summary of the paper
%
In this work we present the potential of \acp{GAN} for
burst \ac{GW} analysis. We have shown that \acp{GAN} have the ability to generate 5
class varieties~\chris{yes, but you make it sound like 5 is special and it's
not} of modelled burst \ac{GW} signals that can be generated at
whim~\chris{really? whim?}. The latent and class spaces were explored through interpolation and
suggest that the space provides smooth translations between classes and overall
waveform shape. We then showed targeted waveform generation by mixing classes
to produce new unmodelled waveform varieties that can be used to test current
burst search pipelines. \jordan{couple of sentences about
classifier}.~\chris{expand this. You have 15-20 pages of material so you can
get a nioce big paragrpah or 2 out of this. It will be repetitive, yes, but
that's the point.}

% extra things to think about
%
In order to extend this work to a viable burst wave generator and classifier a
few points require further research. In principle it is trivial to add another
detector inside the response layer \jordan{response is the wrong thing to say
since the time delay isnt really a response, extrinsic layer? just non
trainable layer? The box?}, however, as this now 3 dimensional signal is feed
to the discriminator this will no doubt require further tweaking of the
network. We can add more burst-like wave forms in the training set, like
detector glitches which would similarly require further network design. The
work presented here is noise free. To havea complete generation and detection
package we would like to train the network on signals hidden in additive
Gaussian noise and test the ability of the auxiliary classifier. 
~\chris{this paragrph is old and out of date. Please unpdate it.}

The approach shown in this work shows promise in generating unmodelled burst
waveforms from exotic~\chris{no} sources. Having the ability to quickly
generate new waveforms is essential to test current detection schemes and their
susceptibilty to unmodelled sources. We believe that \acp{GAN} have the ability
to generate high fidelity waveforms at a fraction of the computational
expense~\chris{don't focus on the expense part since burst waveforms are cheap
anyway} and do not rely on large prior parameter space. Having banks of these
waveforms at hand can aid in our understand of the physics processes behind
these non-standard ac{GW} emitters.  
~\chris{we need to write down paragrph headinsg in the next meeting. I'm tired.}
